---
title: "Experiment with Credit Data"
author: "X. Qu, F. Bilson Darku, & H. Guo"
output:
  html_document:
    highlight: pygments
    theme: cerulean
    toc: yes
    toc_float: yes
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE, include = TRUE, echo = TRUE, 
                      warning = FALSE, fig.keep = 'all'
                      #fig.width = 10, fig.height = 7
                      )
```

## Load Packages
```{r packages, include = TRUE}
source("../R Codes/install_load_packages.R")
```

## Load Custom Functions
```{r custom_functions, include = TRUE}
source("../R Codes/custom_functions.R")
```

## Load and Clean Data
```{r}
# Read data
Data <- read.table("http://archive.ics.uci.edu/ml/machine-learning-databases/statlog/german/german.data")

# Assign column names
names(Data) <- c("CheckingStatus", "Duration_M", "CreditHistory", "Purpose",
                 "CreditAmount", "Savings", "PresentEmploymentSince",
                 "InstallmentRate", "SexMarritalStatus", "Guarantors",
                 "PresentResidenceSince", "Property", "Age", "OtherInstallment",
                 "Housing", "NumExistingCredit", "Job", "NumLiablePeople",
                 "Telephone","ForeignWorker", "CustomerClass")

# List of numerical variables
numerical_atts <- c("Duration_M", "CreditAmount", "InstallmentRate",
                    "PresentResidenceSince", "Age", "NumExistingCredit",
                    "NumLiablePeople")

# List of categorical variables
categorical_atts <- c("CheckingStatus", "CreditHistory", "Purpose", "Savings",
                      "PresentEmploymentSince", "SexMarritalStatus", "Guarantors",
                      "Property", "OtherInstallment", "Housing", "Job", 
                      "Telephone", "ForeignWorker", "CustomerClass")

# List of variables to be selected from the data set
# Select only numerical variables
sub_atts <- c(numerical_atts)

# Select only numerical variables
Data <- Data %>% dplyr::select(all_of(sub_atts))

# Further data cleaning
# Convert currency and character variables to numeric
Data[, numerical_atts] <- Data[, numerical_atts] %>% 
  mutate_if(is.character, parse_number, na = c("", "NA", "na", "$-"))

# Delete missing observations
Data <- Data %>% drop_na()

# Sample 200 records
set.seed(12345)               # Set seed for sampling records
Data <- Data[sample(1:nrow(Data), 200), ]  # Sample rows of data

head(Data)
```

## Experiment Parameters
```{r parameters}
# Confidential variable
conf_var <- "CreditAmount"
  
# Utility variable
pred_var <- "InstallmentRate"

# Masking method
mask_method <- "SADP"

# Model
model <- "LM" 

# Metric
metric <- "R2" 

# Weight for weighted_cost selection method
w <- 0.75

# Change in noise delta 
delta <- 0.3

# Noise level
d <- seq(from = 0.3, to = 6, by = delta)

# Determine if Calculation of Shapley values will be exact or approximate
SV_calc <- (ncol(Data) <= 16) # Exact Shapley value if TRUE, otherwise approximate

# Seed number
seed_number <- 1234
```

```{r prep_param_values, include=FALSE}
# Full name for masking technique
if (mask_method %in% c("SADP", "CADP", "BCADP", "GADP")) {
  mask_method_full <- paste("Additive Pertubation (", mask_method, ")", sep = "")
} else if (mask_method %in% c("MNS1", "MNS2", "LN")) {
  mask_method_full <- paste("Multiplicative Pertubation (", mask_method, ")", sep = "")
} else {
  stop("Incorrect masking method")
}

# Full name for statistical model
full_model_name <- switch(model,
                     LM = "Linear Regression",
                     GLM = "Generalize Linear Model",
                     GAM = "Generalized Additive Model",
                     CART = "Regression Trees")
```

| Parameter | Value |
|----------|------|
|Confidential Variable | `r conf_var`|
|Variable for Prediction Task | `r pred_var`|
|Masking Method | `r mask_method_full`|
|Statistical Model | `r full_model_name`|
|Shapley Value Calculation | `r ifelse(SV_calc, "Exact", "Approximate")`|


```{r initializing, include=TRUE}
# Name of confidential variable after masking
mask_var_name <- paste(conf_var, "Masked", sep = "_")

Data_Masked <- Data %>% mutate((!! mask_var_name) := (!! rlang::sym(conf_var)))
Base_Data <- Data_Masked

# Risk and utility model formulas
risk_model_formula <- as.formula(paste(conf_var, "~ ."))
utility_model_formula <- as.formula(paste(pred_var, "~ ."))

# Memory allocation
k <- length(d)
base_total <- data.frame(noise = d, risk = NA, utility = NA)
base_SV_risk <- data.frame(matrix(NA, ncol = k + 1L, nrow = ncol(Base_Data) - 2L))
colnames(base_SV_risk) <- c("attribute", d)
base_SV_utility <- base_SV_risk
```

## Masking only the Confidential Variable
```{r benchmark_method}
for (i in seq_along(d)){
  
  # Progress
  # print(paste("step:", i, "/", k, sep = ""))
  
  set.seed(seed_number)
  
  # Masking confidential variable(s)
  if (mask_method %in% c("SADP", "CADP", "BCADP")) {
    Base_Data[, mask_var_name] <- ADP(Data[, conf_var],
                                      d = d[i], 
                                      Sigma_e = NULL,
                                      method = mask_method)
  } else if (mask_method == "GADP") {
    Base_Data[, mask_var_name] <- ADP(Data[, conf_var], 
                                      S = dplyr::select(Data, -all_of(pred_var)),
                                      d = d[i], 
                                      Sigma_e = NULL, 
                                      method = mask_method)
  } else if (mask_method %in% c("MNS1", "MNS2", "LN")) {
    Base_Data[, mask_var_name] <- MDP(Data[, conf_var],
                                      d = d[i], 
                                      method = mask_method)
  }

  # Total Disclosure Risk & Utility
  base_total[i, "risk"] <- model_metric(formula = risk_model_formula,
                                        data = dplyr::select(Base_Data, !{{ pred_var }}),
                                        model = model, 
                                        metric = metric)
  
  base_total[i, "utility"] <- model_metric(formula = utility_model_formula,
                                           data = dplyr::select(Base_Data, !{{ conf_var }}),
                                           model = model, 
                                           metric = metric)
  
  # Shapley values for Disclosure Risk & Utility
  if (SV_calc) {# Compute exact Shapley values
    
    SV_Risk <- Shapley.Value(formula = risk_model_formula,
                             data = dplyr::select(Base_Data, !{{ pred_var }}),
                             model = model, 
                             metric = metric)
  
    SV_Utility <- Shapley.Value(formula = utility_model_formula,
                                data = dplyr::select(Base_Data, !{{ conf_var }}),
                                model = model, 
                                metric = metric)
    
  } else {# Approximate Shapley values
    
    SV_Risk <- Shapley.Value.Est(formula = risk_model_formula,
                                 data = dplyr::select(Base_Data, !{{ pred_var }}),
                                 model = model, 
                                 metric = metric)
  
    SV_Utility <- Shapley.Value.Est(utility_model_formula,
                                    data = dplyr::select(Base_Data, !{{ conf_var }}),
                                    model = model, 
                                    metric = metric)
    
  }
  
  
  base_SV_risk[, as.character(d[i])] <- SV_Risk$SV

  base_SV_utility[, as.character(d[i])] <- SV_Utility$SV

}

base_SV_risk$attribute <- base_SV_utility$attribute <- SV_Risk$Variable
```

### Change in distribution of Shapley values (in benchmark method when only masking confidential attributes)

#### Preparing the Results for Graphing
```{r plot_base_frontier,include = TRUE}
# Shapley values for risk
base_SV_risk_long <- tidyr::gather(base_SV_risk,
                                   key = "d",
                                   value = "SV_risk",
                                   paste(d),
                                   factor_key = TRUE)

# Shapley values for utility
base_SV_utility_long <- tidyr::gather(base_SV_utility,
                                      key = "d",
                                      value = "SV_utility",
                                      paste(d),
                                      factor_key = TRUE)

# Combining Risk and Utility
base_SV <- dplyr::full_join(x = base_SV_risk_long, 
                            y = base_SV_utility_long, 
                            by = c("attribute", "d"))

base_SV <- base_SV %>% 
  mutate(attribute = case_match(attribute,
                                "Duration_M" ~ "Duration",
                                "CreditAmount_Masked" ~ "Credit_Mask",
                                "PresentResidenceSince" ~ "Residence",
                                "NumExistingCredit" ~ "NumCredit",
                                "NumLiablePeople" ~ "NumLiable",
                                .default = attribute
                                )
  )
```

#### Figure 4: Two-Dimensional Feature Attribution Based on Shapley Values of Risk and Utility
```{r fig_4}
Feature_Dist <- base_SV %>% 
  filter(d == 2.1) %$%
  frontier_curve(risk = SV_risk, 
               utility = SV_utility,
               attribute_labels = attribute, 
               frontier = "none",
               plot_labels = "all",
               output = "graph",
               facet_var = d)

print(Feature_Dist)
```

#### Figure 5a: Risk-Utility Frontier (Noise = 2.1) 
```{r fig_5a}
mask_var_name <- "Credit_Mask"

base_SV_graph_5a <- base_SV %>% 
  filter(d == 2.1) %$%
  frontier_curve(risk = SV_risk, 
                 utility = SV_utility,
                 attribute_labels = attribute, 
                 frontier = "upper",
                 plot_labels = "all",
                 output = "graph",
                 special_points = mask_var_name,
                 facet_var = d)

# Print frontier
print(base_SV_graph_5a)
```

#### Figure 5b: Risk-Utility Frontier (Noise = 3.6)
```{r fig_5b}
base_SV_graph_5b <- base_SV %>% 
  filter(d == 3.6) %$% 
  frontier_curve(risk = SV_risk, 
                 utility = SV_utility,
                 attribute_labels = attribute, 
                 frontier = "upper",
                 plot_labels = "all",
                 output = "graph",
                 special_points = mask_var_name,
                 facet_var = d)

# Print frontier
print(base_SV_graph_5b)
```

#### Figure 6: Feature Selection Criteria and Corresponding Tangent Lines (Noise = 2.4)
```{r fig_7}
special_points <- mask_var_name

base_SV_graph_6 <- base_SV %>% 
  filter(d == 2.4) %$%
  frontier_curve(risk = SV_risk, 
                 utility = SV_utility, 
                 attribute_labels = attribute, 
                 frontier = "upper",
                 plot_labels = "all", 
                 output = "data", 
                 special_points = mask_var_name, 
                 facet_var = d)

base_SV_graph_6 <- base_SV_graph_6 %>%
  mutate(RU_ratio = risk/utility, 
         risk_std = risk/sum(risk),
         utility_std = utility/sum(utility),
         WC = w*risk_std - (1-w)*utility_std,
         point_shape = attribute %in% special_points)

max_risk_std <- max(base_SV_graph_6$risk_std)
max_ru_ratio <- max(base_SV_graph_6$RU_ratio)
max_wc <- max(base_SV_graph_6$WC)

# Normalize Scale
tangent_normalized_wc <- base_SV_graph_6 %>% 
  ggplot() +
  geom_point(aes(x = utility_std, y = risk_std, shape = point_shape), 
             color = "blue") +
  geom_text_repel(mapping = aes(x = utility_std, y = risk_std, label = attribute),
                 alpha = 0.6, size = 3) +
  geom_line(mapping = aes(x = utility_std, y = risk_std, linetype = "a", color = "a"),
            data = filter(base_SV_graph_6, dominated == FALSE)) +
  geom_hline(aes(yintercept = max_risk_std, linetype = "b", color = "b"), 
             show.legend = TRUE) +
  geom_abline(aes(intercept = max_wc/w, 
                  slope = (1 - w)/w, linetype = "c", color = "c"), show.legend = FALSE) +
  theme_bw() +
  scale_shape_manual(name = "Feature",
                     values = c(16, 1), 
                     labels = c("Non Confidential", "Confidential (Masked)"),
                     limits = c(FALSE, TRUE)) +
  guides(shape = guide_legend(override.aes = list(linetype = 0, color = "black"))) +
  scale_linetype_manual(name = "Line",
                        limits = c("a", "b", "c"),
                        values = c("solid", "dashed", "dotted"),
                        labels = c("Frontier",
                                   bquote(italic(t)[risk]),
                                   bquote(italic(t)[wc]~group("(", omega == .(w),")"))
                                   )
                        ) +
  scale_colour_manual(name = "Line",
                      limits = c("a", "b", "c"),
                      labels = c("Frontier",
                                 bquote(italic(t)[risk]),
                                 bquote(italic(t)[wc]~group("(", omega == .(w),")"))
                                 ),
                      values = c("red", "green4", "brown", "violet"),
                      ) +
  labs(x = "Shapley Value of Utility for Features (normalized)",
       y = "Shapley Value of Risk for Features (normalized)"
  ) 

tangent_normalized_wc
```
