---
title: "Experiment with IS Salary Data"
author: "X. Qu, F. Bilson Darku, & H. Guo"
output:
  html_document:
    highlight: pygments
    theme: cerulean
    toc: yes
    toc_float: yes
editor_options: 
  chunk_output_type: console
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE, include = TRUE, echo = TRUE, 
                      warning = FALSE, fig.keep = 'all'
                      #fig.width = 10, fig.height = 7
                      )
```

## Load Packages
```{r packages}
source("../R Codes/install_load_packages.R")
```

## Load Custom Functions
```{r custom_functions}
source("../R Codes/custom_functions.R")
```

## Load and Clean Data
```{r dataset}
# Load the data set.
Data <- read_csv("https://www.dropbox.com/s/zz4lbj0qqlvizas/Salary_Data.csv?dl=1",
                 col_names = c("Year", "SeqNumber", "identity", "Yrs_exp", 
                               "Education", "Top_J_Pubs", "Ref_J_Pubs",
                               "Textbooks", "Research_Books", "Other_Pubs",
                               "Salary", "Summer", "summer_yrs", "res_budget",
                               "move_supp", "tch_load", "Tenure_Req_Lvl", 
                               "Tenure_Req_A", "Tenure_Req_tot", "Position",
                               "location", "pub_prvt", "Union", "Country",
                               "Region", "schl_deg", "accredit", 
                               "Accepted_ornot", "Tch/Res", "%_Summer",
                               "%_Budget", "tot_J pubs"),
                 skip = 1)

# List of numerical variables
numerical_atts <- c("Yrs_exp", "Top_J_Pubs", "Ref_J_Pubs", "Textbooks",
                    "Research_Books", "Other_Pubs", "Salary", "Summer", 
                    "summer_yrs", "res_budget", "move_supp", 
                    "Tenure_Req_Lvl", "Tenure_Req_A", "Tenure_Req_tot")

# List of categorical variables
categorical_atts <- c("Year", "Education", "Position", "pub_prvt", "schl_deg", 
                      "tch_load", "accredit")

# List of variables to be selected from the data set
sub_atts <- c(numerical_atts, categorical_atts)

# Select only numerical variables
Data <- Data %>%  dplyr::select(all_of(sub_atts))

# Further data cleaning
# Convert currency and character variables to numeric
Data[, numerical_atts] <- Data[, numerical_atts] %>% 
  mutate_if(is.character, parse_number, na = c("", "NA", "na", "$-"))

# Convert categorical variables into factors
Data[, categorical_atts] <- Data[, categorical_atts] %>% 
  mutate_if(is.character, as.factor)

# Make sure all numerical attributes are valid
Data <-  Data[, numerical_atts]  %>% dplyr::select(-Research_Books, -Textbooks) 
# Delete missing observations
Data <- Data %>% drop_na()
```


## Experiment Parameters
```{r parameters, include=FALSE}
# Confidential variable
conf_var <- "Salary"
  
# Utility variable
pred_var <- "res_budget"

# Masking method
mask_method <- "BCADP"

# Model
model <- "LM"

# Metric
metric <- "R2"

# Selection technique
sel_method <- "risk_only"
w <- 0.75 # weight for risk when using weighted_cost

# Change in noise delta 
delta <- 0.3

# Noise level
d <- seq(from = 0.3, to = 3, by = delta)

# Determine if Calculation of Shapley values will be exact or approximate
SV_calc <- (ncol(Data) <= 16) # Exact Shapley value if TRUE, otherwise approximate

# Seed number
seed_number <- 1252
```

```{r prep_param_values, include=FALSE}
# Full name for masking technique
if (mask_method %in% c("SADP", "CADP", "BCADP", "GADP")) {
  mask_method_full <- paste("Additive Pertubation (", mask_method, ")", sep = "")
} else if (mask_method %in% c("MNS1", "MNS2", "LN")) {
  mask_method_full <- paste("Multiplicative Pertubation (", mask_method, ")", sep = "")
} else {
  stop("Incorrect masking method")
}

# Full name for statistical model
full_model_name <- switch(model,
                     LM = "Linear Regression",
                     GLM = "Generalize Linear Model",
                     GAM = "Generalized Additive Model",
                     CART = "Regression Trees")

# Full name for selection technique
sel_method_full <- switch(sel_method, 
                          weighted_cost = paste("Highest Total Cost with w_risk = ", w),
                          risk_only = "Highest Risk")
```

| Parameter | Value |
|----------|------|
|Confidential Variable | `r conf_var`|
|Variable for Prediction Task | `r pred_var`|
|Masking Method | `r mask_method_full`|
|Statistical Model | `r full_model_name`|
|Attribute Selection Method |`r sel_method_full`|
|Shapley Value Calculation | `r ifelse(SV_calc, "Exact", "Approximate")`|


```{r initializing}
# Name of confidential variable after masking
mask_var_name <- paste(conf_var, "Masked", sep = "_")

Data_Masked <- Data %>% mutate((!! mask_var_name) := (!! rlang::sym(conf_var)))
Base_Data <- Data_Masked

# Risk and utility model formulas
risk_model_formula <- as.formula(paste(conf_var, "~ ."))
utility_model_formula <- as.formula(paste(pred_var, "~ ."))

# Memory allocation
k <- length(d)
base_total <- data.frame(noise = d, risk = NA, utility = NA)
base_SV_risk <- data.frame(matrix(NA, ncol = k + 1L, nrow = ncol(Base_Data) - 2L))
colnames(base_SV_risk) <- c("attribute", d)
base_SV_utility <- base_SV_risk
```

## Masking only the Confidential Variable
```{r benchmark_method}
for (i in seq_along(d)){
  
  # Progress
  # print(paste("step:", i, "/", k, sep = ""))
  
  set.seed(seed_number)
  
  # Masking confidential variable(s)
  if (mask_method %in% c("SADP", "CADP", "BCADP")) {
    Base_Data[, mask_var_name] <- ADP(Data[, conf_var],
                                      d = d[i], 
                                      Sigma_e = NULL,
                                      method = mask_method)
  } else if (mask_method == "GADP") {
    Base_Data[, mask_var_name] <- ADP(Data[, conf_var], 
                                      S = select(Data, -all_of(pred_var)),
                                      d = d[i], 
                                      Sigma_e = NULL, 
                                      method = mask_method)
  } else if (mask_method %in% c("MNS1", "MNS2", "LN")) {
    Base_Data[, mask_var_name] <- MDP(Data[, conf_var],
                                      d = d[i], 
                                      method = mask_method)
  }

  # Total Disclosure Risk & Utility
  base_total[i, "risk"] <- model_metric(formula = risk_model_formula,
                                        data = select(Base_Data, !{{ pred_var }}),
                                        model = model, 
                                        metric = metric)
  
  base_total[i, "utility"] <- model_metric(formula = utility_model_formula,
                                           data = select(Base_Data, !{{ conf_var }}),
                                           model = model, 
                                           metric = metric)
  
  # Shapley values for Disclosure Risk & Utility
  if (SV_calc) {# Compute exact Shapley values
    
    SV_Risk <- Shapley.Value(formula = risk_model_formula,
                             data = select(Base_Data, !{{ pred_var }}),
                             model = model, 
                             metric = metric)
  
    SV_Utility <- Shapley.Value(formula = utility_model_formula,
                                data = select(Base_Data, !{{ conf_var }}),
                                model = model, 
                                metric = metric)
    
  } else {# Approximate Shapley values
    
    SV_Risk <- Shapley.Value.Est(formula = risk_model_formula,
                                 data = select(Base_Data, !{{ pred_var }}),
                                 model = model, 
                                 metric = metric)
  
    SV_Utility <- Shapley.Value.Est(utility_model_formula,
                                    data = select(Base_Data, !{{ conf_var }}),
                                    model = model, 
                                    metric = metric)
    
  }
  
  
  base_SV_risk[, as.character(d[i])] <- SV_Risk$SV

  base_SV_utility[, as.character(d[i])] <- SV_Utility$SV

}

base_SV_risk$attribute <- base_SV_utility$attribute <- SV_Risk$Variable
```

### Change in distribution of Shapley values
```{r plot_base_frontier}
# Shapley values for risk
base_SV_risk_long <- tidyr::gather(base_SV_risk,
                                   key = "d",
                                   value = "SV_risk",
                                   paste(d),
                                   factor_key = TRUE)

# Shapley values for utility
base_SV_utility_long <- tidyr::gather(base_SV_utility,
                                      key = "d",
                                      value = "SV_utility",
                                      paste(d),
                                      factor_key = TRUE)

# Combining Risk and Utility
base_SV <- dplyr::full_join(x = base_SV_risk_long, 
                            y = base_SV_utility_long, 
                            by = c("attribute", "d"))

```

### Risk-Utilily Map
```{r plot_base_RU_map}
base_RU_map <- base_total %>% 
  mutate(across(c("risk", "utility"),  \(x) lead(x, n = 1), .names = "{.col}_b")) %>%
  ggplot(aes(x = utility, y = risk)) + 
  geom_point(color = "blue") +
  geom_text(mapping = aes(label = d), hjust = 0.1, vjust = 1) +
  geom_segment(aes(xend = utility_b, yend = risk_b), color = "blue",
               arrow = arrow(length = unit(0.20, "cm"))) +
  labs(x = "Data Utility",
       y = "Disclosure Risk") +
  theme_bw()

print(base_RU_map)
```


## Proposed Methods
Find frontier curve to identify potential confidential attribute
```{r plot_initial_frontier, include = TRUE}
init_SV_fc <- base_SV %>% 
  filter(d == d[1]) %$%
  frontier_curve(risk = SV_risk,
                 utility = SV_utility,
                 attribute_labels = attribute,
                 special_points = mask_var_name)

# Potential attribute: Numerical attributes that are located on the frontier
potential_nonconfi_att <- init_SV_fc %>% 
  filter(dominated == FALSE, attribute %in% numerical_atts) %>% 
  select(attribute) %>% pull()
```

Numerical attributes that are located on the initial frontier: **`r paste(potential_nonconfi_att, collapse=", ")`**

### High Disclosure Risk Selection Method
```{r memory_allocation_3}
# Memory allocation
each_frontier_total <- data.frame(candidate_att = "Updated Efficient Frontier",
                            masked_att = NA,
                            noise_conf = NA,
                            noise_nonconf = NA,
                            noise_total = d, 
                            risk = NA, 
                            utility = NA)
each_frontier_SV_risk <- data.frame(matrix(NA, nrow = (ncol(Data) - 1L), ncol = k + 2L))
colnames(each_frontier_SV_risk) <- c("candidate_att", "attribute", d)
each_frontier_SV_risk$candidate_att <- "Updated Efficient Frontier"

each_frontier_SV_utility <- each_frontier_SV_risk
```


```{r each_frontier_masking_risk_only}
each_frontier <- c(conf_var, potential_nonconfi_att)
d_all <- numeric(ncol(Data))
names(d_all) <- colnames(Data)
  
each_frontier_Data <- Data_Masked

for (i in seq_along(d)) {
  
  ## Progress
  # print(paste("step:", i, "/", k, sep = ""))
  
  if (i == 1) {
    
    next_att <- conf_var
    d_all[next_att] <- d[i]
    
  } else {

    d_all[next_att] <- d_all[next_att] + delta

  }
    
  if (next_att == conf_var) {
    # Name of confidential variable after masking
    mask_var_name <- paste(next_att, "Masked", sep = "_")
  } else {
    mask_var_name <- next_att
  }  
    
 
  each_frontier_total[i, "masked_att"] <- next_att
  each_frontier_total[i, "noise_conf"] <- d_all[conf_var]
    
  set.seed(seed_number)
    
  # Masking variable(s)
  if (mask_method %in% c("SADP", "CADP", "BCADP")) {
    each_frontier_Data[, mask_var_name] <- ADP(Data[, next_att],
                                         d = d_all[next_att], 
                                         Sigma_e = NULL,
                                         method = mask_method)
  } else if (mask_method == "GADP") {
    each_frontier_Data[, mask_var_name] <- ADP(Data[, next_att], 
                                         S = select(Data, -all_of(pred_var)),
                                         d = d_all[next_att], 
                                         Sigma_e = NULL, 
                                         method = mask_method)
  } else if (mask_method %in% c("MNS1", "MNS2", "LN")) {
    each_frontier_Data[, mask_var_name] <- MDP(Data[, next_att],
                                         d = d_all[next_att], 
                                         method = mask_method)
  }
    
  # Total Disclosure Risk & Utility
  each_frontier_total[i, "risk"] <- model_metric(formula = risk_model_formula,
                                               data = select(each_frontier_Data, 
                                                             -all_of(pred_var)),
                                               model = model, 
                                               metric = metric)
    
  each_frontier_total[i, "utility"] <- model_metric(formula = utility_model_formula,
                                                  data = select(each_frontier_Data, 
                                                                -all_of(conf_var)),
                                                  model = model, 
                                                  metric = metric)
    
  # Shapley values for Disclosure Risk & Utility
  if (SV_calc) {# Compute exact Shapley values
    
    SV_Risk <- Shapley.Value(formula = risk_model_formula,
                             data = select(each_frontier_Data, -all_of(pred_var)),
                             model = model,
                             metric = metric)
      
    SV_Utility <- Shapley.Value(formula = utility_model_formula,
                                data = select(each_frontier_Data, -all_of(conf_var)),
                                model = model, 
                                metric = metric)
      
  } else {# Approximate Shapley values
    
    SV_Risk <- Shapley.Value.Est(formula = risk_model_formula,
                                 data = select(each_frontier_Data, -all_of(pred_var)),
                                 model = model, 
                                 metric = metric)
      
    SV_Utility <- Shapley.Value.Est(utility_model_formula,
                                    data = select(each_frontier_Data, -all_of(conf_var)),
                                    model = model, 
                                    metric = metric)
      
  }
    
  
  each_frontier_SV_risk[, as.character(d[i])] <- SV_Risk$SV
    
  each_frontier_SV_utility[, as.character(d[i])] <- SV_Utility$SV
  
  each_frontier_comb_SV <- full_join(x = SV_Risk, 
                                     y = SV_Utility, 
                                     by = "Variable") %>%
    select(Variable, SV.x, SV.y) %>%
    rename(SV_Risk = SV.x, SV_Utility = SV.y)
    
  if (sel_method == "weighted_cost") {
    each_frontier_comb_SV <- each_frontier_comb_SV %>% 
      mutate((!! sel_method) := w*SV_Risk /(sum(SV_Risk)) - (1 - w)*SV_Utility/(sum(SV_Utility)))
  } else if (sel_method == "risk_only") {
    each_frontier_comb_SV <- each_frontier_comb_SV %>% 
      mutate((!! sel_method) := SV_Risk/mean(SV_Risk)*100)
  } else {
    stop("Select an appropriate 'sel_method'")
  }
  
  # Finding the frontier
  each_frontier_SV_fc <- each_frontier_comb_SV %$% 
    frontier_curve(risk = SV_Risk,
                   utility = SV_Utility,
                   attribute_labels = Variable,
                   output = "data",
                   special_points = mask_var_name)
  
  # Looking for all the points on the frontier
  each_frontier_comb_SV_d <- left_join(x = each_frontier_comb_SV, 
                                       y = each_frontier_SV_fc,
                                       by = c("Variable" = "attribute")) %>%
    select(Variable, dominated, {{sel_method}})
  
  # Finding the next attribute to mask
  next_att <- each_frontier_comb_SV_d %>% 
    mutate(Variable = str_remove(Variable, "_Masked")) %>%
    filter(dominated == FALSE, Variable %in% c(numerical_atts)) %>%
    slice_max(across({{ sel_method }}), with_ties = FALSE) %>%
    select(Variable) %>%
    pull()
  
}

each_frontier_SV_risk[, "attribute"] <- SV_Risk$Variable
each_frontier_SV_utility[, "attribute"] <- SV_Utility$Variable

each_frontier_total <- each_frontier_total %>% 
  mutate(noise_nonconf = noise_total - noise_conf)
```


#### Figure 8a: Comparing Benchmark with Risk-Only Masking Approaches
```{r plot_comparing_methods}
# Expanding the base method results to look like that of two_att_total
base_total_ex <- base_total %>% 
  rename(noise_total = noise) %>%
  add_column(candidate_att = paste(conf_var, "only"),
             masked_att = conf_var,
             .before = "noise_total") %>%
  mutate(noise_conf = noise_total, noise_nonconf = 0, .before = "noise_total")

# Stacking the results of base method on top of two_att_total
All_Risk_Utility_Tradeoff <- bind_rows(base_total_ex, each_frontier_total)


# Plotting and comparing risk-utility tradeoff map
graph_all <- All_Risk_Utility_Tradeoff %>% 
  mutate(candidate_att = ifelse(candidate_att == "Updated Efficient Frontier", "Proposed (risk)", candidate_att)) %>%
  mutate(candidate_att = ifelse(candidate_att == "Salary only", "Benchmark", candidate_att)) %>%#
  group_by(candidate_att) %>%
  mutate(across(c("risk", "utility"),  \(x) lead(x, n = 1), .names = "{.col}_b")) %>%
  ungroup() %>%
  mutate(masked_att = factor(masked_att, levels = c("Salary", "Summer", "move_supp"), labels = c("Salary", "Summer", "Move_Supp"))) %>%    #change the order of legend
  ggplot(aes(x = utility, y = risk, group = candidate_att)) + 
  geom_point(aes(colour = candidate_att, shape = masked_att), size = 3) +
  geom_text(mapping = aes(label = noise_total), hjust = 0.2, vjust = 1.2) +
  geom_segment(aes(xend = utility_b, yend = risk_b,  linetype = candidate_att, colour = candidate_att),
               arrow = arrow(length = unit(0.20, "cm"))) +
  scale_color_manual(values =  c("Benchmark" = "blue", "Proposed (risk)" = "red" )) +
  scale_shape_manual(values =  c("Salary" = 16 ,"Summer" = 15, "Move_Supp" = 17)) +
  labs(x = "Data Utility",
       y = "Disclosure Risk",
       linetype = "Method",
       colour = "Method",
       shape = "Masked Feature") +
  theme_bw() +
  guides(colour = guide_legend(override.aes = list(shape = NA)))

print(graph_all)
```

### Weighted-Cost Selection Method
```{r reset_param_values_for_weighted_cost}
sel_method <- "weighted_cost" 

# Name of confidential variable after masking
mask_var_name <- paste(conf_var, "Masked", sep = "_")

Data_Masked <- Data %>% mutate((!! mask_var_name) := (!! rlang::sym(conf_var)))
Base_Data <- Data_Masked
```

```{r each_frontier_masking_weighted_cost}
each_frontier <- c(conf_var, potential_nonconfi_att)
d_all <- numeric(ncol(Data))
names(d_all) <- colnames(Data)
  
each_frontier_Data <- Data_Masked

for (i in seq_along(d)) {
  
  ## Progress
  # print(paste("step:", i, "/", k, sep = ""))
  
  if (i == 1) {
    
    next_att <- conf_var
    d_all[next_att] <- d[i]
    
  } else {

    d_all[next_att] <- d_all[next_att] + delta

  }
    
  if (next_att == conf_var) {
    # Name of confidential variable after masking
    mask_var_name <- paste(next_att, "Masked", sep = "_")
  } else {
    mask_var_name <- next_att
  }  
    
 
  each_frontier_total[i, "masked_att"] <- next_att
  each_frontier_total[i, "noise_conf"] <- d_all[conf_var]
    
  set.seed(seed_number)
    
  # Masking variable(s)
  if (mask_method %in% c("SADP", "CADP", "BCADP")) {
    each_frontier_Data[, mask_var_name] <- ADP(Data[, next_att],
                                         d = d_all[next_att], 
                                         Sigma_e = NULL,
                                         method = mask_method)
  } else if (mask_method == "GADP") {
    each_frontier_Data[, mask_var_name] <- ADP(Data[, next_att], 
                                         S = select(Data, -all_of(pred_var)),
                                         d = d_all[next_att], 
                                         Sigma_e = NULL, 
                                         method = mask_method)
  } else if (mask_method %in% c("MNS1", "MNS2", "LN")) {
    each_frontier_Data[, mask_var_name] <- MDP(Data[, next_att],
                                         d = d_all[next_att], 
                                         method = mask_method)
  }
    
  # Total Disclosure Risk & Utility
  each_frontier_total[i, "risk"] <- model_metric(formula = risk_model_formula,
                                               data = select(each_frontier_Data, 
                                                             -all_of(pred_var)),
                                               model = model, 
                                               metric = metric)
    
  each_frontier_total[i, "utility"] <- model_metric(formula = utility_model_formula,
                                                  data = select(each_frontier_Data, 
                                                                -all_of(conf_var)),
                                                  model = model, 
                                                  metric = metric)
    
  # Shapley values for Disclosure Risk & Utility
  if (SV_calc) {# Compute exact Shapley values
    
    SV_Risk <- Shapley.Value(formula = risk_model_formula,
                             data = select(each_frontier_Data, -all_of(pred_var)),
                             model = model, 
                             metric = metric)
      
    SV_Utility <- Shapley.Value(formula = utility_model_formula,
                                data = select(each_frontier_Data, -all_of(conf_var)),
                                model = model, 
                                metric = metric)
      
  } else {# Approximate Shapley values
    
    SV_Risk <- Shapley.Value.Est(formula = risk_model_formula,
                                 data = select(each_frontier_Data, -all_of(pred_var)),
                                 model = model, 
                                 metric = metric)
      
    SV_Utility <- Shapley.Value.Est(utility_model_formula,
                                    data = select(each_frontier_Data, -all_of(conf_var)),
                                    model = model, 
                                    metric = metric)
      
  }
    
  
  each_frontier_SV_risk[, as.character(d[i])] <- SV_Risk$SV
    
  each_frontier_SV_utility[, as.character(d[i])] <- SV_Utility$SV
  
  each_frontier_comb_SV <- full_join(x = SV_Risk, 
                                     y = SV_Utility, 
                                     by = "Variable") %>%
    select(Variable, SV.x, SV.y) %>%
    rename(SV_Risk = SV.x, SV_Utility = SV.y)
    
  if (sel_method == "weighted_cost") {
    each_frontier_comb_SV <- each_frontier_comb_SV %>% 
      mutate((!! sel_method) := w*SV_Risk /(sum(SV_Risk)) - (1 - w)*SV_Utility/(sum(SV_Utility)))
  } else if (sel_method == "risk_only") {
    each_frontier_comb_SV <- each_frontier_comb_SV %>% 
      mutate((!! sel_method) := SV_Risk/mean(SV_Risk)*100)
  } else {
    stop("Select an appropriate 'sel_method'")
  }
  
  # Finding the frontier
  each_frontier_SV_fc <- each_frontier_comb_SV %$% 
    frontier_curve(risk = SV_Risk,
                   utility = SV_Utility,
                   attribute_labels = Variable,
                   output = "data",
                   special_points = mask_var_name)
  
  # Looking for all the points on the frontier
  each_frontier_comb_SV_d <- left_join(x = each_frontier_comb_SV, 
                                       y = each_frontier_SV_fc,
                                       by = c("Variable" = "attribute")) %>%
    select(Variable, dominated, {{sel_method}})
  
  # Finding the next attribute to mask
  next_att <- each_frontier_comb_SV_d %>% 
    mutate(Variable = str_remove(Variable, "_Masked")) %>%
    filter(dominated == FALSE, Variable %in% c(numerical_atts)) %>%
    slice_max(across({{ sel_method }}), with_ties = FALSE) %>%
    select(Variable) %>%
    pull()
  
}

each_frontier_SV_risk[, "attribute"] <- SV_Risk$Variable
each_frontier_SV_utility[, "attribute"] <- SV_Utility$Variable

each_frontier_total <- each_frontier_total %>% 
  mutate(noise_nonconf = noise_total - noise_conf)
```


#### Figure 8b: Comparing Benchmark and Weighted-Cost Masking Approaches
```{r plot_comparing_methods_wc}
# Expanding the base method results to look like that of two_att_total
base_total_ex <- base_total %>% 
  rename(noise_total = noise) %>%
  add_column(candidate_att = paste(conf_var, "only"),
             masked_att = conf_var,
             .before = "noise_total") %>%
  mutate(noise_conf = noise_total, noise_nonconf = 0, .before = "noise_total")

# Stacking the results of base method on top of two_att_total
All_Risk_Utility_Tradeoff <- bind_rows(base_total_ex, each_frontier_total)


# Plotting and comparing risk-utility tradeoff map
graph_all <- All_Risk_Utility_Tradeoff %>% 
   mutate(candidate_att = ifelse(candidate_att == "Updated Efficient Frontier", "Proposed (wc)", candidate_att)) %>%
  mutate(candidate_att = ifelse(candidate_att == "Salary only", "Benchmark", candidate_att)) %>%#
  group_by(candidate_att) %>%
  mutate(across(c("risk", "utility"),  \(x) lead(x, n = 1), .names = "{.col}_b")) %>%
  ungroup() %>%
  mutate(masked_att = factor(masked_att, levels = c("Salary", "Summer", "move_supp"), labels = c("Salary", "Summer", "Move_Supp"))) %>%    #change the order of legend
  ggplot(aes(x = utility, y = risk, group = candidate_att)) + 
  geom_point(aes(colour = candidate_att, shape = masked_att), size = 3) +
  geom_text(mapping = aes(label = noise_total), hjust = 0.2, vjust = 1.2) +
  geom_segment(aes(xend = utility_b, yend = risk_b,  linetype = candidate_att, colour = candidate_att),
               arrow = arrow(length = unit(0.20, "cm"))) +
  scale_color_manual(values = c("Benchmark" = "blue", "Proposed (wc)" = "red")) +
  scale_shape_manual(values = c("Salary" = 16 ,"Summer" = 15, "Move_Supp" = 17)) +
  labs(x = "Data Utility",
       y = "Disclosure Risk",
       linetype = "Method",
       colour = "Method",
       shape = "Masked Feature") +
  theme_bw() +
  guides(colour = guide_legend(override.aes = list(shape = NA)))


print(graph_all)
```